Stack Safety is a Security Property

### 2021-04-17 tex/main.tex
wibble

More interesting (from a stack safety perspective) changes to the tags
happen at exactly the points in the program where we switch from a
caller to a callee or vice-versa:

>>>>

More interesting changes to the tags (from a stack safety perspective) 
happen at exactly the points in the program where we switch from a
caller to a callee or vice-versa:
